MSAD_PCA_Walkthrough

### 2017-01-25 Simulation_Vignette.Rmd
CURRENT ISSUE: Number of alarmed and non-alarmed observations can be less than or even greater than the number of training observations. WTF?

# Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
falseAlarmRate_SPE <- sum(results_ls$FaultChecks[,5] %in% c(2,3)) /
  nrow(results_ls$FaultChecks)
# The SPE false alarm rate hits 0 at alpha = 0.07.
falseAlarmRate_T2 <- sum(results_ls$FaultChecks[,5] %in% c(1,3)) /
  nrow(results_ls$FaultChecks)
# The T2 false alarm rate hits 0 at alpha = 0.00015, and is at 16% at 0.07. The
# T2 statistic throws too many false alarms for my taste.

# Why don't we have 10080 - 2880 rows in the Alarm matrix?? We need to set the
# simulation run so that this mspMonitor function crawls over all 10080 rows.
# Right now, the code does not "learn" after each run. At each updateFreq, we
# need the function to append the non-alarmed test data to the training data,
# and then rerun mspMonitor on the next updateFreq observations.
```

>>>>

# Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
falseAlarmRate_SPE <- sum(results_ls$FaultChecks[,5] %in% c(2,3)) /
  nrow(results_ls$FaultChecks)
# The SPE false alarm rate hits 0 at alpha = 0.07.
falseAlarmRate_T2 <- sum(results_ls$FaultChecks[,5] %in% c(1,3)) /
  nrow(results_ls$FaultChecks)
# The T2 false alarm rate hits 0 at alpha = 0.00015, and is at 16% at 0.07. The
# T2 statistic throws too many false alarms for my taste.
# These values were before we split the update observations by a third. These
# false alarm rates increased dramatically (0.19, 0.41), so we increased the 
# number of training observations to 4320 (three days worth, up from 2880). The
# false alarm rates dropped back, but not nearly as low (0.0031, 0.0884).

# CURRENT ISSUE: The number of alarmed and non-alarmed observations does not
# sum to 10080 - trainObs. For 2880 training observations, the sum of alarmed
# and non-alarmed observations was 83 + 4195 = 4278 < 10080 - 2880 = 7200,
# while for 4320 training observations, the sum was 506 + 5256 = 5762 > 10080 -
# 4320 = 5760. What in the actual hell?
```
